---
title: "ROC#4_2"
output: html_document
date: "2025-03-03"
---


```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

if (!require("dplyr")) {install.packages("dplyr"); require("dplyr")}
if (!require("Seurat")) {install.packages("Seurat"); require("Seurat")}
if (!require("patchwork")) {install.packages("patchwork"); require("patchwork")}
if (!require("cowplot")) {install.packages("cowplot"); require("cowplot")}
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
if (!require("plotly")) {install.packages("plotly"); require("plotly")}
if (!require("knitr")) {install.packages("knitr"); require("knitr")}
if (!require("htmlwidgets")) {install.packages("htmlwidgets"); require("htmlwidgets")}
if (!require("here")) {install.packages("here"); require("here")}
if (!require("EnhancedVolcano")) {BiocManager::install('EnhancedVolcano'); require("EnhancedVolcano")} # volcano plot
if (!require("tidyverse")) {install.packages("tidyverse"); require("tidyverse")} # for titying up data
if (!require("RColorBrewer")) {install.packages("RColorBrewer"); require("RColorBrewer")} # for color brewer
if (!require("sctransform")) {install.packages("sctransform"); require("sctransform")} # for data normalization
if (!require("glmGamPoi")) {BiocManager::install('glmGamPoi'); require("glmGamPoi")} # for data normalization, sctransform
if (!require("openxlsx")) {install.packages("openxlsx"); require("openxlsx")} # to save .xlsx files
if (!require("SoupX")) {install.packages("SoupX"); require("SoupX")}
if (!require("DoubletFinder")) {BiocManager::install('DoubletFinder'); require("DoubletFinder")}
library(plotly)
library(ggvenn)
library(gplots)

set.seed((12345))
here()

```

s
```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.align = 'center'}


Dataset <- LoadSeuratRds("Dataset2.rds")
Singlets <- LoadSeuratRds("Singlets.rds")

Doublets <- LoadSeuratRds("Doublets.rds")

```




I think I need to find a way to make the rownames barcodes so they can match up with barcodes of other objects so make both Dataset and Singlets barcodes


March 3th. 

I had some help regarding this problem and was able to merge everything and give it its own unique variable name

New approach to this is to explain every code and what it is doing + why to further understand coding and my process.

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

# I believe I need to analyze the Datasets again and Identify each cluster into more depth so higher resolution is needed. 

# Im going to start by superclustering Singlets dataset to see what we have.

Singlets <- FindNeighbors(Singlets, dims = 1:15)
Singlets <- FindClusters(Singlets, resolution = 2)

Singlets <- RunUMAP(Singlets, dims = 1:15)

DimPlot(Singlets, reduction = "umap")

Doublets <- FindNeighbors(Doublets, dims = 1:15)
Doublets <- FindClusters(Doublets, resolution = 2)

Doublets <- RunUMAP(Doublets, dims = 1:15)

DimPlot(Doublets, reduction = "umap")

# Now that I have both of their clusters I need to rename them at 2 levels. 
# For Identification Im going to use the Pipeline for Multidimensional Plot
```

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

DimPlot(Singlets, reduction = "umap") + ggtitle("Singlets") + theme(plot.title = element_text(hjust = 0.5))

markers.to.plot1 <- c("Lrp2",         # PT
                      "Slc5a12",     # PT-S1
                      "Slc13a3",     # PT-S2
                      "Slc16a9",     # PT-S3
                      "Havcr1",      # Injured PT
                      "Epha7",       # dTL
                      "Slc12a1",     # TAL
                      "Cldn10",      # TAL
                      "Cldn16",      # TAL
                      "Nos1",        # MD
                      "Slc12a3",     # DCT
                      "Pvalb",       # DCT1
                      "Slc8a1",      # DCT2, CNT
                      "Aqp2",        # PC
                      "Slc4a1",      # IC-A
                      "Slc26a4",     # IC-B
                      "Upk1b",       # Uro
                      "Ncam1",       # PEC
                      "Pdgfrb",      # Perivascular
                      "Piezo2",      # Mesangial
                      "Pdgfra",      # Fib
                      "Acta2",       # Mural
                      "Nphs1",       # Podo
                      "Kdr",         # Capillary Endo
                      "Lyve1",       # Lymph
                      "Ptprc",       # Immune
                      "Cd74",        # Macrophage
                      "Skap1"        # B/T Cells
)

DotPlot(Singlets,
        features = markers.to.plot1,
        dot.scale = 8,
        dot.min = 0,
        scale.max = 100,
        scale.min = 0,
        col.min = -2.5,
        col.max = 2.5)+
  coord_flip()

```
```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

Singlets@meta.data <- Singlets@meta.data %>% mutate(subclass = dplyr::case_when(
  seurat_clusters == 0 ~ "PTS2",
  seurat_clusters == 1 ~ "PTS1",
  seurat_clusters == 2 ~ "TAL",
  seurat_clusters == 3 ~ "PTS3",
  seurat_clusters == 4 ~ "EC",
  seurat_clusters == 5 ~ "EC/Mes",
  seurat_clusters == 6 ~ "PTS2a",
  seurat_clusters == 7 ~ "PTS2b",
  seurat_clusters == 8 ~ "DCT",
  seurat_clusters == 9 ~ "PTS2c",
  seurat_clusters == 10 ~ "PTS1a", # check this
  seurat_clusters == 11 ~ "DCTa",
  seurat_clusters == 12 ~ "FIB/PERI",
  seurat_clusters == 13 ~ "DTL",
  seurat_clusters == 14 ~ "TALa",
  seurat_clusters == 15 ~ "PTS1",
  seurat_clusters == 16 ~ "PC",
  seurat_clusters == 17 ~ "PCa",
  seurat_clusters == 18 ~ "PTS2d",
  seurat_clusters == 19 ~ "PT",
  seurat_clusters == 20 ~ "ICA",
  seurat_clusters == 21 ~ "DTLa",
  seurat_clusters == 22 ~ "ICB",
  seurat_clusters == 23 ~ "DCTb",
  seurat_clusters == 24 ~ "macrophage/immune",
  seurat_clusters == 25 ~ "PERI",
  seurat_clusters == 26 ~ "URO",
  seurat_clusters == 27 ~ "PODO",
  seurat_clusters == 28 ~ "PTS3a",
  seurat_clusters == 29 ~ "PC",

))

Idents(Singlets) <- Singlets@meta.data$subclass
DimPlot(Singlets, reduction = "umap", label = T)
VlnPlot(Singlets, "nFeature_RNA")


Singlets@meta.data <- Singlets@meta.data %>% mutate(class = dplyr::case_when(
  seurat_clusters == 0 ~ "PT",
  seurat_clusters == 1 ~ "PT",
  seurat_clusters == 2 ~ "TAL",
  seurat_clusters == 3 ~ "PT",
  seurat_clusters == 4 ~ "EC",
  seurat_clusters == 5 ~ "EC",
  seurat_clusters == 6 ~ "PT",
  seurat_clusters == 7 ~ "PT",
  seurat_clusters == 8 ~ "DCT",
  seurat_clusters == 9 ~ "PT",
  seurat_clusters == 10 ~ "PT", # check this
  seurat_clusters == 11 ~ "DCT",
  seurat_clusters == 12 ~ "FIB/PERI",
  seurat_clusters == 13 ~ "DTL",
  seurat_clusters == 14 ~ "TAL",
  seurat_clusters == 15 ~ "PT",
  seurat_clusters == 16 ~ "PC",
  seurat_clusters == 17 ~ "PC",
  seurat_clusters == 18 ~ "PT",
  seurat_clusters == 19 ~ "PT",
  seurat_clusters == 20 ~ "IC",
  seurat_clusters == 21 ~ "DTL",
  seurat_clusters == 22 ~ "IC",
  seurat_clusters == 23 ~ "DCT",
  seurat_clusters == 24 ~ "macrophage/immune",
  seurat_clusters == 25 ~ "FIB/PERI",
  seurat_clusters == 26 ~ "URO",
  seurat_clusters == 27 ~ "PODO",
  seurat_clusters == 28 ~ "PT",
  seurat_clusters == 29 ~ "PC",

))

Idents(Singlets) <- Singlets@meta.data$class
DimPlot(Singlets, reduction = "umap", label = T)
VlnPlot(Singlets, "nFeature_RNA")

```


```{r}


DimPlot(Singlets, reduction = "umap", label = T)
DimPlot(Doublets, reduction = "umap", label = T)
DimPlot(Dataset, reduction = "umap", label = T)

# I have 3 different seurat object, I've played around and tried a lot but my problem is merging the metadata. 

# Not sure why Dataset, Became the same thing as my Singlets Data
```


```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}


# this command turns the meta.data of object = Singlets into a dataframe. 
# Doing this will help me merge my two Datasets. 
metadata1 <- Singlets@meta.data
metadata1
metadata2 <- Dataset@meta.data
metadata2

# To view things with a venn , Data must be a list of values instead of a dataframe so you have to take the identification of each row which are genes are turn it into a list of names

list_1 <- rownames(metadata1)
list_2 <- rownames(metadata2)
#creats an object named venn with ggvenn naming them meta1 and meta 2 for both lists
venn <- ggvenn(list(meta1 = list_1, meta2 = list_2))
venn




lst <- list(list_1,list_2)
item_list <- venn(lst, show.plot = TRUE)
test <- attributes(item_list)$intersections
test$A


df2 <- test$B
df2 <- as.data.frame(df2)
df2$unique <- "unique2"
df3 <- df2 %>% column_to_rownames(var = "df2")
datasetb <- AddMetaData(Dataset, df3) 

# df4 = dataframe of R Pipeline uniqueness
df4 <- test$A
# as.data.frame turns it back into a dataframe instead of a value list.
df4 <- as.data.frame(df4)

# creates a new metadata column called unique and puts "unique" for all columns. 
df4$unique <- "unique" 
df5 <- df4 %>% column_to_rownames(var = "df4")

# Check overlap between row names of df5 and column names of Dataset
overlap <- intersect(rownames(df5), colnames(Dataset))

# Print the overlapping names
print(overlap)

# Count the number of overlapping entries
cat("Number of overlapping entries:", length(overlap), "\n")

# 0 overlapping entries , why??


# d5 now has the genes listed as the rownames so it is ready to be merged
singletb <- AddMetaData(Singlets, df5) 
#NO cell overlap between new meta data and seurat Object. Works with Singlet Dataset not "Dataset"
# this now merged the word unique to the metadata of Singlets, I now want to add to different codes 

# unique = unique on new Pipeline side
# unique2 = unique on manual side.
# same = both R and I were on the same page :)

#df2,df3 = Dataset testa , datasetb
#df4,df5 = Singlet testb , singletb
#df6,df7 = BOTH testab , same_gene

df6 <- test$`A:B`
df6 <- as.data.frame(df6)
df6$unique <- "same"
df7 <- df6 %>% column_to_rownames(var = "df6")
same_gene <- AddMetaData(Dataset, df7) 

# ask AI
colnames(Dataset)
colnames(datasetb@meta.data)[colnames(datasetb@meta.data) == "subclass.l2"] <- "subclass"

head(same_gene@meta.data)
head(singletb@meta.data)
head(datasetb@meta.data)
#these 3 are all seurat objects 
DimPlot(singletb, reduction = "umap",group.by = "class", split.by = "unique")
DimPlot(same_gene, reduction = "umap",group.by = "class", split.by = "unique")
DimPlot(datasetb, reduction = "umap", group.by = "class", split.by = "unique")

rm(df2,df3,df4,df5,df6,df7)


#datasetb has a metadata column called subclass.l2 I need to change it to just subclass
# d5 now has the genes listed as the rownames so it is ready to be merged 



```

March 3 7:05pm

Taking a break now, From the venn diagram and test chart I gave each section (3) a metadata column called unique based on if they're the same unique on my side or unique from the Soupx side.

I need to find a way to bring it all together and view it well.
```{r}

# Rename metadata column in datasetb
colnames(datasetb@meta.data)[colnames(datasetb@meta.data) == "subclass.l2"] <- "subclass"

# Merge Seurat objects
merged_obj <- merge(
  x = singletb,
  y = list(same_gene, datasetb),
  add.cell.ids = c("Singlet", "SameGene", "DatasetB")
)

# Verify merged object
print(merged_obj)
head(merged_obj@meta.data)

mem.maxVSize(56000)

# Perform normalization and visualization
merged_obj <- NormalizeData(merged_obj, normalization.method = "LogNormalize", scale.factor = 10000)
merged_obj <- FindVariableFeatures(merged_obj, selection.method = "vst", nfeatures = 2000)
merged_obj.genes <- rownames(merged_obj)
merged_obj <- ScaleData(merged_obj, features = merged_obj.genes)
merged_obj <- RunPCA(merged_obj, features = VariableFeatures(object = merged_obj))
merged_obj <- FindNeighbors(merged_obj, dims = 1:15)
merged_obj <- FindClusters(merged_obj, resolution = 0.1)
merged_obj <- RunUMAP(merged_obj, dims = 1:15)

DimPlot(merged_obj, reduction = "umap", group.by = "class", split.by = "unique")
DimPlot(merged_obj, reduction = "umap", group.by = "unique", split.by = "unique")
library(plotly)

dim_plot <- DimPlot(merged_obj, reduction = "umap", group.by = "class", split.by = "unique") +
  ggtitle("UMAP Dimensional Reduction")
interactive_plot <- ggplotly(dim_plot)
interactive_plot
```